Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-01-20 awipev-CO2.Rmd
update SNAPO graph2

at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5,valueRange = c(-25, 30)) %>%
    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

>>>>

at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
